%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{ifthen}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
  \ifthenelse{\equal{#1}{}}{
    {#2}}{\textbf{#1}{: #2}}
  \vspace{-1pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\ifthenelse{\equal{#1}{}}{}{\item}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \ifthenelse{\equal{#1}{}}{}{\textbf{#1} & #2 \\}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://firmanhp.com/blog/}{\Large Firman Hadi Prayoga}} & Email: firmanhp.91 at gmail dot com\\
  \href{https://firmanhp.com/blog}{https://firmanhp.com/blog} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rapsodo}{Singapore}
      {Senior Software Engineer}{Jan 2026 - Present}
      \resumeItemListStart
      \resumeItem{Technologies}{Linux, C++17/20, Iceoryx IPC, Buildroot, Breakpad, LVGL}
        \resumeItem{}{Owned the end to end system integration of an upcoming sports analytics hardware aimed for baseball players.}
        \resumeItem{}{Implemented the LCD screens on the device using LVGL.}
        \resumeItem{}{Diagnosed silent memory leaks and identified CPU-hogging threads via heap profiling, resolving stability and performance regressions.}
        \resumeItem{}{Brought up the performance profiling ecosystem (Linux perf, Perfetto) for the software stack.}
        \resumeItem{}{Built several tools to improve developer experience in the company:
          \resumeItemListStart
            \resumeItem{}{\href{https://github.com/firmanhp/sysprop}{\color{blue}sysprop}: Runtime/persistent
                          global scope system properties storage, to easily modify program behavior without having to recompile or
                          restarting the service.}
            \resumeItem{}{\href{https://github.com/firmanhp/crashomon}{\color{blue}crashomon}: An out-of-process offline
                          crash monitoring and reporting ecosystem which wraps Google Crashpad to produce crash minidumps to
                          be pulled from the device later for developer analysis.}
          \resumeItemListEnd
        }
      \resumeItemListEnd
    \resumeSubheading
      {Google}{New Taipei City, Taiwan}
      {Senior Software Engineer, Pixel Camera System Software}{Feb 2021 - Dec 2025}
      \resumeItemListStart
        \resumeItem{Technologies}
          {Android Native, Linux kernel, Perfetto, perf/simpleperf, C++17/20, Java, Soong, Bazel,
           I$^2$C/I$^3$C}
        % \resumeItem{}
        %   {Recognized internally for proactively supporting team's code quality by conducting
        %    thorough design reviews and promoting adherence to the company's C++ programming
        %    best practices. Mentored several newcomers on the development workflow.}
        \resumeItem{}
          {Collaborated with cross-functional teams to deliver multiple features in
          unified Camera HAL for Google Tensor SoCs:
            \resumeItemListStart
            % \resumeItem{}{Image Stabilization (Implemented hardware lens position data sampling to improve the algorithm's accuracy.)}
            \resumeItem{}{Super Res Zoom (worked on calibration data infrastructure and image stabilization experience on high zoom),}
            \resumeItem{}{Face Unblur (reduced CPU power usage by 100mW by cutting off unnecessary calculations, extending battery life),}
            \resumeItem{}{Camera2 Settings override API (reduced zoom experience latency by 1 frame = 33.3ms),}
            \resumeItem{}{Third party camera support (improved the JPEG compression time from 80ms to 40ms via scheduler tuning),}
            \resumeItem{}{Dual camera concurrent streaming (designed the support pipeline infrastructure to support two cameras streaming at 10FPS/30FPS)}
            \resumeItemListEnd
           }
        \resumeItem{}
          {Owned software driver design, Linux device tree definitions, and power sequences
           for early bring-up of camera hardware modules on Pixel devices, including experimental hardware.}
        \resumeItem{}
           {Directed cross-layer software development for confidential technology prototypes,
            establishing software guidelines and constructing integrated software solutions
            encompassing kernel-level design and userspace integration.}
        \resumeItem{}
           {Drove system health improvements across the Camera software stack:
            \resumeItemListStart
            \resumeItem{}{Built an automated Perfetto trace ingestion and metrics dashboard pipeline, allowing systematic
            latency regression detection across camera pipeline stages.}
            \resumeItem{}{Improved the memory allocation-deallocation pattern in one of our processing pipelines, reducing
            per-frame memory from 300MiB to 4MiB by reusing memory segments.}
            \resumeItem{}{Designed a low-overhead continuous performance telemetry system using reservoir sampling
            to bound memory usage at runtime, enabling always-on latency monitoring without impacting the streaming
            pipeline.}
            \resumeItemListEnd
            
          }
        % \resumeItem{Pixel early camera module bring-up}
        %   {Responsible for the bringup process of various camera peripherals for Google Pixel
        %    7/8/9 series, this includes the EEPROM, PMIC device drivers and the Linux device
        %    tree definitions (power sequence, I$^2$C bus configuration).}
        % \resumeItem{Pixel Zoom Experience Improvement}
        %   {Designed, and implemented the first version of API implementation for
        %    Camera2 API request settings override. achieved 1 frame zoom latency
        %    improvement in 30FPS streaming (33.3ms).}
        % \resumeItem{Testing}
        %   {Developed end-to-end use case test suites in Java to proactively
        %    identify and mitigate potential regressions during early development stages.}
        % \resumeItem{JPEG compression}
        %   {Improved the performance of our JPEG compression pipeline (libjpeg) through tweaking the
        %    process affinity and core clocks. Reduced JPEG compression time from 80ms to 40ms,
        %    enabling faster image output for third party consumer applications.}
        % \resumeItem{Pixel Face Unblur}
        %   {Reduced the CPU power usage by around 100mW by reviewing the pipeline and eliminating
        %    unnecessary CPU processings steps. This means more efficient performance and extended
        %    battery life for users.}
        % \resumeItem{Hardware data sampling}
        %   {Implemented a lens position sampling from hardware, as part of image processing
        %    algorithm quality improvements.}
        % \resumeItem{Development workflow improvement}
        %   {Introduced an improvement to the bring-up workflow by doing a remote bringup
        %    using SSH through the factory servers located outside Taiwan. This not only
        %    gained recognition from leadership but also delivered cost savings by eliminating
        %    the need for in-person travel.}
        % \resumeItem{\href{https://blog.google/products/pixel/super-res-zoom-google-pixel/}{Pixel Super Res Zoom}}
        %   {Built a scalable infrastructure for image processing algorithms to fetch on device
        %    calibration data stored in EEPROM, and the infrastructure of multi camera
        %    streaming pipeline. The design is still used in current generation Pixel camera HALs.}
        % \resumeItem{Pixel 15x Zoom}
        %   {Designed, and provided the infrastructure to let the application get the wider FOV
        %    preview with image stabilization to help users point the camera on high level zoom.}
      \resumeItemListEnd

    \resumeSubheading
      {Center of Computer Science, University of Indonesia}{Depok, Indonesia}
      {Software Engineering Intern}{Jan 2020 - Feb 2020}
      \resumeItemListStart
      % \resumeItem{Technologies}{Java, Java Spring, OAuth, Apereo CAS, Python, Django}
      % \resumeItem{}
      %   {Built a Java Spring project starter template that supports user and role management
      %     and authentication through multiple OAuth providers (Google, Facebook, Twitter, etc),
      %     including university's single sign on system out of the box.}
      % \resumeItem{}{Created an interface for Apereo CAS (Java) to verify user credentials stored in database managed by Django administration.}
      \resumeItem{}{Built a Java Spring template with multi-provider OAuth support and integrated Apereo CAS for credential verification against a Django-managed database.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Singapore}
      {Software Engineering Intern, Google Pay}{June 2019 - Aug 2019}
      \resumeItemListStart
      % \resumeItem{Technologies}{Android, Dagger, Java}
      % \resumeItem{}
      % {The internship spans around 3 months of doing a single project.
      %  The team was focused on GPay India Merchant application using Java
      %  with an in-house framework designed for low performance Android phones.}
      % \resumeItem{}
      %   {Designed and implemented an experience improvement to the merchant onboarding process
      %   by letting merchants scan their PAN card (Indian Tax ID) and autofills the form using OCR.}
      \resumeItem{}{Designed and implemented a PAN card OCR feature to streamline merchant onboarding on Google Pay Android.}
      \resumeItemListEnd

  \resumeSubheading
      {Qlapa}{Jakarta, Indonesia}
      {Software Engineering Intern}{June 2017 - Aug 2017, June 2018 - Aug 2018}
      \resumeItemListStart
      % \resumeItem{Technologies}{Java, Java Play Framework, Scala, Elasticsearch, Redis, Apache Airflow, MySQL, phpMyAdmin, Python, pandas, numpy, pyplot}
      % \resumeItem{}{Introduced Apache Airflow for the first time in the system for ETL purposes.}
      % \resumeItem{}{Extended the product's discount system to support shipping discount on top of product discount.}
      % \resumeItem{}{Implemented the new design for the merchant's product creation page.}
      % \resumeItem{}{Improved the server backend system's health by introducing bugfixes and refactors.}
      \resumeItem{}{Introduced Apache Airflow for ETL pipelines; extended discount system and improved backend health via bugfixes and refactors.}
      \resumeItemListEnd
  
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal Side Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/firmanhp/sysprop}{\color{blue}sysprop}}
    {Android-inspired, Linux-based runtime/persistent system properties storage, to easily modify program
     behavior without having to recompile or restarting the service. Useful to hide features under
     development or testing before officially releasing. Written in C++20.}
  \resumeSubItem{\href{https://github.com/firmanhp/crashomon}{\color{blue}crashomon}}
    {An offline based crash reporting ecosystem based on Google Crashpad and Breakpad, consisting of three main tools:
     Client, Watcher, and Analyzer. A crashing process will produce a small minidump (hundreds of KBs) in which
     stack can be traced using the Analyzer tool. The minidump produced is magnitudes smaller than a Linux coredump so it can
     be manually pulled to the cloud for developer analysis. Written in both C++20 and Python.}
  \resumeSubItem{\href{https://github.com/firmanhp/anthropic_original_performance_takehome}{\color{blue}Anthropic's performance take home test}}
    {Optimized a program running on a toy VLIW ISA, minimizing CPU cycles. Hand-tuned instruction sequences and built a systematic instruction scheduler,
     achieving 71x speedup (147,000 → 2,044 cycles).}
  \resumeSubItem{\href{https://github.com/firmanhp/osdev}{\color{blue}OSDev}}
    {An ongoing toy bare metal program running on Raspberry Pi 3 Model B (AArch64),
     as part of exploring the Rust programming language. Currently
     implemented basic hardware feature support like UART, GPIO, ARM Mailboxes.
     Utilized debugging using QEMU, GDB, objdump, and a little bit of Ghidra. Features
     being explored include interrupts, virtual memory, and graphics output.
     Project logs are documented in \href{https://firmanhp.com/blog}{\color{blue}personal blog} and inside
     the repository.}
  % \resumeSubItem{\href{https://firmanhp.com/blog}{\color{blue}Personal Blog}}
  %    {Personal blog built using NextJS static web pages.}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Languages}{C++, Rust, Java, Python, Javascript, SQL}
  \resumeSubItem{Technologies}{
    Linux,
    Android,
    Cargo,
    PostgreSQL,
    MySQL,
    Django,
    ExpressJS,
    OAuth,
    % Apereo CAS,
    % Dagger,
    % Java Play Framework,
    Elasticsearch,
    Redis,
    Apache Airflow,
    % phpMyAdmin,
    pandas,
    numpy,
    % pyplot,
    Android Native,
    Perfetto,
    perf/simpleperf,
    Soong,
    Bazel,
    I$^2$C/I$^3$C,
    QEMU,
    GDB,
    objdump,
    Ghidra,
    ARM (AArch64),
    Buildroot,
    Iceoryx IPC,
    Breakpad,
    LVGL
  }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Indonesia}{Indonesia}
      {Bachelor of Science in Computer Science;  GPA: 3.95 / 4.00}{Aug. 2016 -- Aug. 2020}
    \resumeItemListStart
      \resumeItem{Notable courses taken}{Information Retrieval, Machine Learning, Data Science \& Analytics,
        Numerical Analysis, Competitive Programming, Operating Systems, Systems Programming}
      \resumeItem{Extracurricular activities}{Part of RISTEK (students club focusing on
        specific competitive subjects) in Competitive Programming, and Data Science}
      % \resumeItem{Event committee}{Part of committee on several student-held events such as CompFest 9, CompFest X.
      %   CompFest is the largest student-held computer event in Indonesia}
      \resumeItem{}
        {Participated in several competitive programming contests, mainly ACM-ICPC (now called ICPC):
        \resumeItemListStart
            \resumeItem{National Gold Medalist}{2018 ACM-ICPC Asia Jakarta}
            \resumeItem{National Silver Medalist}{2019 ACM-ICPC Asia Jakarta}
            \resumeItem{7th Place}{2017 ACM-ICPC Asia Ho Chi Minh City}
            \resumeItem{Honorable mention}{2017 ACM-ICPC Asia Jakarta}
            \resumeItem{Honorable mention}{2018 ACM-ICPC Asia Nakhon Pathom}
            \resumeItem{Fourth place}{Indonesia National Contest 2017}
            \resumeItem{10th Place}{Indonesia National Contest 2019}
            \resumeItem{Second Place}{Competitive Programming Arkavidia 5.0}
            \resumeItem{Fourth place}{Compfest 8 Senior Competitive Programming Contest}
            \resumeItem{Fourth place}{Compfest 11 Senior Competitive Programming Contest}
            \resumeItemListEnd
        }
          
    \resumeItemListEnd
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}